---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# treemixTools

<!-- badges: start -->
<!-- badges: end -->

The goal of treemixTools is to visualize treemix result with ggplot2 packages

## Installation

You can install the development version of treemixTools from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("thehung92/treemixTools")
```

## Example

This code load the treemix result from the package external data. Now my library can be load with a single `library` function call

```{r}
library(treemixTools)
library(tidyverse)
library(patchwork)
#
infiles <- system.file('extdata', package='treemixTools') |> list.files(full.names=TRUE)
inStem <- infiles[1] |> gsub(pattern=".cov.gz", replacement="")
obj <- read_treemixResult(inStem)
names(obj)
```

## plot the graph with ggtree

```{r graph, fig.height=3, fig.width=6}
fig.tree <- plot_treemix_graph(obj)
fig.tree
```

## plot the drift params heatmap

```{r drift, fig.height=3, fig.width=6}
fig.drift <- plot_treemix_drift(obj)
fig.drift
```

## plot the residual heatmap 

```{r residual, fig.height=3, fig.width=6}
fig.resid <- plot_treemix_residual(obj)
fig.resid
```

## merge

```{r merge, fig.height=7, fig.width=6}
fig.tree + fig.drift + fig.resid +
  plot_layout(ncol=1, nrow=3) +
  plot_annotation(tag_levels = 'A') & theme(legend.justification = "left")
```

