---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# treemixTools

<!-- badges: start -->
<!-- badges: end -->

The goal of treemixTools is to ...

## Installation

You can install the development version of treemixTools from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("thehung92/treemixTools")
```

## Example

This code load the treemix result from the package external data

```{r example}
library(tidyverse)
library(treedataverse)
library(treemixTools)
#
infiles <- system.file('extdata', package='treemixTools') |> list.files(full.names=TRUE)
inStem <- infiles[1] |> gsub(pattern=".cov.gz", replacement="")
obj <- read_treemixResult(inStem)
str(obj)
```

## plot the graph with ggtree

```{r}
plot_treemix_graph(obj)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>
